Arbitrary Precision and Arbitrary $n$-Grams

### 2011-03-01 paper/paper.Rnw
minor capitalization
perplexity experiment should work
colors and remove unigrams from plot
colors
paper

\documentclass{article}
\newcommand{\osn}{\oldstylenums}
\title{Arbitrary Precision and Arbitrary $n$-grams}
\author{Alec Story and Thomas Levine\\\small{avs\osn{38} and tkl\osn{22}}}

@@

	\\

@@

@@

@@

	\subsection*{Perplexity of generated sentences}

\begin{figure}
\begin{center}
<<echo=F,fig=T,height=9>>=
par(mfrow=c(2,1))
pp_gen.plot(results.shakespeare,'Shakespeare')
pp_gen.plot(results.tolstoy,'War and Peace')
@
\end{center}
\end{figure}

>>>>

\documentclass{article}
\newcommand{\osn}{\oldstylenums}
\title{Arbitrary Precision and Arbitrary $n$-Grams}
\author{Alec Story and Thomas Levine\\\small{avs\osn{38} and tkl\osn{22}}}

\newcommand\ngram{$n$-gram}
\newcommand\loga{logarithmic arithmetic}

@@

	%\\

@@

	%We trained our system on the \emph{Shakespeare} and \emph{War and Peace} corpora.

@@

\section*{Experimental design}
We trained our model on the training data and then
ran two experiments to study the effect of \ngram length and
probability computation type on perplexity on the two corpora.
The two probability computation types were arbitrary precision
arithmetic and \loga.
For each experiment, we tested \ngram length of $n$=$1$ to $5$.

We hypothesized that longer $n$-grams would yield lower perplexity
and that the two probability computation types would yield similar perplexity.

\subsection*{Perplexity of test set}
We evaluated our model on the test set by computing
the perplexity of the test set. In addition to the variables
above, we ran this test with smoothing on and with smoothing off.
We hypothesized that smoothing would reduce perplexity.

\subsection*{Perplexity of generated sentences}
We also evaluated our model on sentences generated by our model.
We did this because sentence generation involves substantial
probability computations, where the difference in probability
computation type would be relevant.

For each combination of the intependent variables, we
generated 23 sentences from the \emph{War and Peace} corpus
and tested their perplexity. %ADD SHAKESPEARE

@@

\subsection*{Perplexity of generated sentences}
Perplexity of generated sentences decreased with increased
\ngram length

\begin{figure}
\begin{center}
<<echo=F,fig=T,height=9>>=
par(mfrow=c(2,1))
pp_gen.plot(results.shakespeare,'Shakespeare')
pp_gen.plot(results.tolstoy,'War and Peace')
@
\end{center}
\caption{\label{fig:gen}Perplexities of generated sentences by $n$-gram length and probability computation method for the two corpora.}
\end{figure}
